% Chapter Template

\chapter{Conclusion} % Main chapter title

\label{Chapter8} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}


\section{Summary}

TODO summarize the goals from the Introduction and broadly describe
what techniques were most helpful in reaching them. Also detail a
summary of exactly how effective they were.

\section{Answering Research Questions}
\label{sec:answering-research-questions}

\subsection{Feasibility on Consumer Hardware}
\label{subsec:answer-feasibility}

\emph{What are the constraints for a sound-based smart cube design
compatible with consumer-grade microphones like those found in common
smartphones and laptops?}

As discussed in Chapter \ref{Chapter4}, there are four main factors
that affect the viability of a sound-based smart cube design: the
achievable signal-to-noise ratio of the transmitter, the
distinctiveness of the tones used for the protocol, the frequency
response range of the consumer hardware used to implement the protocol,
and the range of tones audible to the human ear.

An analysis of these factors found that the tones used in the protocol
should be spaced at least 100Hz apart and broadcast with an audio
intensity of -30dB or greater in order to have a sufficiently strong
signal-to-noise ratio for clear detection. Furthermore, the specific
tones chosen for the protocol would ideally fit within the "musical
range" of 500Hz and 4000Hz to simultaneously avoid irritating human
solvers and leverage the optimizations built into consumer audio
recording hardware in smartphones and laptops.

\subsection{Move Tracking Accuracy}
\label{subsec:answer-accuracy}

\emph{How could a sound-based smart cube design track the face turns of
a Rubik's Cube with high accuracy?}

As discussed in Section \ref{sec:move-tracking-accuracy}, the receiver
from Chapter \ref{Chapter5} and the transmitter from Chapter
\ref{Chapter6} were able to transmit and decode a sequence of face
turns with perfect accuracy across a variety of input parameters within
a controlled environment. \footnote{Specifically, this controlled
environment consisted of synthetically generated audio representative
of the output of an ideal transmitter (see Sections
\ref{sec:synthetic-audio-generation} and
\ref{sec:adding-realistic-noise}) played from a Google Pixel phone and
recorded by an HP Spectre laptop in a quiet room (see Section
\ref{subsec:signal-to-noise-ratio}).}

Various factors aided in these results. First, each face position is
associated with a signal present in a unique frequency band (See
Section \ref{subsec:tone-distinctiveness}). This separation of
frequencies makes it easier to distinguish changes in the state of
independent faces on the cube. Second, the current position of each
face is continuously broadcast, increasing the amount of time available
for the receiver to detect and decode each position over time (See
Section \ref{sec:alternatives}). Third, multiple layers of noise
reductions were applied within the receiver to better focus on the true
signal frequencies and boost confidence in the accuracy of the decoded
face turns (See Section \ref{sec:decoding-realistic-noise}).


\subsection{Compatibility with Standard Speedcubes}
\label{subsec:answer-compatibility}

\emph{How could a sound-based smart cube design be deployed within a
standard, "non-smart" speedcube without requiring permanent
modifications to the original cube?}

The key challenges involved in creating a sound-based smartcube
enhancement for an existing speedcube stem from the size constraints
imposed by the structure of the cube. Since all modifications must be
non-destructive, the required electronics must be embedded into the
empty spaces within the cubies on the cube. Furthermore, since neither
the edges nor the corners on the cube have access to the axles on which
the cube rotates, the best place for these electronics is within the
centercaps themselves. Unfortunately, these centercaps offer little
space for add-ins. For example, as discussed in Sections
\ref{subsec:prospects-of-miniaturization} and
\ref{sec:miniaturization}, the relatively spacious Gans 356 only offers
space for a $16mm^2$ PCB with rounded corners and a $6mm$ diameter hole
in the middle.

Despite these stringent size constraints, Chapter \ref{Chapter6}
specifies a promising transmitter design consisting of less than 10
discrete electrical components. With this limited component count, a
PCB consisting of SMD components would be able to fit within a
custom-printed centercap for a Gans 356 speedcube as shown in Figure
\ref{fig:core-placement}.\footnote{Note that an actual PCB was not
constructed nor was a PCB layout attempted for any other cube than the
Gans 356.}

As discussed in Section
\ref{sec:compatibility-with-standard-speedcubes}, since the required
electronics are contained within a replaceable, custom centercap, the
modifications can be easily reversed by replacing the custom centercaps
with the originals.


\subsection{Move Tracking Granularity}
\label{subsec:answer-granularity}

\emph{How could a sound-based smart cube design record the time spent
executing each individual face turn of a Rubik's Cube?}

The receiver proposed in Chapter \ref{Chapter5} decodes face turns by
iterating over a time series of audio data. As a result, when a face
turn is detected, the receiver also knows the time at which it
occurred. By computing the difference between the times at which two
successive turns occurred, the time spent executing an individual face
turn can be computed. Thus, as long as the receiver can detect the face
turns applied to the cube with high accuracy, then the time spent
executing each one can be easily calculated (See also Section
\ref{sec:move-tracking-granularity}).


\subsection{Competition Legality}
\label{subsec:answer-competition-legality}

\emph{How could a sound-based smartcube design comply with competition
regulations prohibiting the use of electronics while performing a
competitive solve?}

Since the use of electronics while competitively solving a Rubik's Cube
is banned by WCA regulation 2i \cite{wca-regulations}, any move
tracking solutions must not permanently embed electronics into the
structure of the cube.

The solution proposed in Section
\ref{subsec:prospects-of-miniaturization} is to create a tiny sound
transmitter that can be embedded into a custom centercap. Such a
transmitter can be temporarily installed during personal practice then
replaced with the original centercaps during competitions.

Alternatively, since the signal of a sound-based transmitter can be
blocked by by a physical wall or purposefully broadcasting interfering
signals in the same frequency range, it's possible that, with proper
negotiation with the WCA, a sound based move tracking solution could be
deemed competition legal.


\section{Limitations}
\label{sec:limitations}

As stated in Section \ref{sec:research-questions}, the overarching goal
of this thesis is to present a proof-of-concept for a sound-based smart
cube design. Like all proofs-of-concept, the design proposed in this
thesis contains some inherent flaws and underlying assumptions that limit
its ability to be successfully deployed in existing speedcubes.

First, while Chapter \ref{Chapter6} demonstrates that its proposed
transmitter design appropriately considers all relevant requirements, a
fully functional transmitter was never built and deployed within an
existing speedcube. As such, the viability of this transmitter design
cannot be fully verified until a transmitter is fully constructed,
deployed, and tested.

Second, while great care was taken to extensively test the receiver,
all tests were conducted with realistic, but synthetic audio samples
since a physical transmitter was never built (See Section
\ref{sec:adding-realistic-noise}). As such, it is possible that further
refinements to the receiver will be required if the signals from a real
transmitter substantially differ from those synthesized for testing the
receiver.

Third, though not a functional limitation, since the typical frequency
response range of consumer hardware is entirely within the human
auditory range (see Sections \ref{subsec:frequency-response-range} and
\ref{subsec:human-auditory-range}), all frequencies selected for
transmitting the state of the cube will be human-audible. If the chosen
frequencies are higher in pitch (as recommended by Section
\ref{subsec:freq-selection}), the sounds produced by the transmitter
may prove irritating to the speedcuber. 

- \textbf{TODO There were perfect parameters for each scramble, but how do we know which parameters to use for an arbitrary scramble?}


\section{Outlook}
\label{sec:outlook}
TODO If I had more time/resources to work on it, what would I do next
with this project?

- Live algorithm
- build it small enough to fit in the cube.
- supersonic frequencies.